### 2020-06-24 README.Rmd
:pen:
update mode

```{r}
raw_files <- neon_index(table = "brd_countdata-expanded")
raw_files
```

@@

```{r message=FALSE, eval=FALSE}
write.csv(raw_files, "index.csv")
zip("brd_countdata.zip", raw_files$path)
```

>>>>

```{r}
raw_files <- neon_index(table = "brd_countdata-expanded", hash="md5")
raw_files
```

@@

```{r message=FALSE}
write.csv(raw_files, "index.csv")
zip("brd_countdata.zip", raw_files$path)
```
